Evaluating a simplified forecast model in comparison to the ECDC forecasting hub ensemble

### 2022-05-26 docs/paper/paper.Rmd
figure tuning

# Load ECDC forecasts. See data-raw/get-hub-forecasts.R for munging
# Merge with truth and rescale to incidence rate per 100,000
forecasts <- fread(here("data", "forecasts.csv")) |>
  merge_forecasts_with_truth(truth) |>
  rescale_to_incidence_rate(population, scale = 1000)
```

@@

```{r vis-forecasts}
locs <- c("United Kingdom", "Germany", "Slovakia", "Italy")

forecasts[location_name %in% locs] |>
  DT(, date := target_end_date) |>
    plot_predictions(
      by = c("horizon", "location_name"), range = c(30, 60, 90)
    ) +
    facet_rep_grid(
      location_name ~ horizon, scales = "free_y", repeat.tick.labels = "y"
    ) +
    aes(fill = model, col = model) +
    scale_y_continuous(labels = comma) +
    scale_fill_brewer(palette = "Dark2") +
    scale_color_brewer(palette = "Dark2") +
    labs(x = "Date", fill = "Model", col = "Model", ramp = "Range")
```

>>>>

# Load ECDC forecasts. See data-raw/get-hub-forecasts.R for munging
# Merge with truth and rescale to incidence rate per 100,000
forecasts <- fread(here("data", "forecasts.csv")) |>
  merge_forecasts_with_truth(truth) |>
  rescale_to_incidence_rate(population, scale = 1e4)
```

@@

```{r vis-forecasts}
locs <- c("United Kingdom", "Germany", "Slovakia", "Italy", "Poland", "Greece")

forecasts[location_name %in% locs] |>
  DT(, date := target_end_date) |>
    plot_predictions(
      by = c("horizon", "location_name"), range = c(30, 60, 90)
    ) +
    facet_grid(
      location_name ~ horizon) +
    aes(fill = model, col = model) +
    scale_y_log10(labels = comma, oob = squish, limits = c(0.1, 1000)) +
    scale_fill_brewer(palette = "Dark2") +
    scale_color_brewer(palette = "Dark2") +
    labs(x = "Date", fill = "Model", col = "Model", ramp = "Range")
```
